RNA-seq from 4 cell populations

### 2021-08-02 deconvolution/fans4/molec_profiling.Rmd
bug fix

#### Batch corrected
```{r PCA.batch, fig.width=10, fig.height=5}
fit = dream(geneExpr, ~ (1|Batch), info)

@@

# different because only genes expressed in given cell type are used
res_cv_FANS = lapply(CTarray, function(CT){

>>>>

#### Batch corrected
```{r PCA.batch, fig.width=10, fig.height=5}
fit = dream(geneExpr, ~ (1|Batch), info, BPPARAM=SnowParam(12, progressbar=TRUE))

@@

# different because only genes expressed in given cell type are used
res_cv_FANS = lapply( unlist(CTarray), function(CT){
